# Extracting Tweet Entities

## Problem

You want to extract tweet entities such as `@mentions`, `#hashtags`, and short URLs from Twitter search results or other batches of tweets.

## Solution

Use `rtweet::search_tweets()` or any of the _timeline_ functions in `rtweet`.

## Discussion

Michael has provided a very powerful search interace for Twitter data mining. `rtweet::search_tweets()` retrieves, parses and extracts an asounding amount of data for you to then use. Let's search Twitter for the `#rstats` hashtag and see what is available:

```{r 03_pkgs, message=FALSE, warning=FALSE, cache=TRUE}
library(rtweet)
library(tidyverse)
```
```{r 03_search, message=FALSE, warning=FALSE, cache=TRUE}
(rstats <- search_tweets("#rstats", n=300)) # pull 300 tweets that used the "#rstats" hashtag

glimpse(rstats)
```

From the output, you can see that all the URLs (short and expanded), status id's, user id's and other hashtags are all available and all in a [tidy](http://r4ds.had.co.nz/tidy-data.html) data frame. 

What are the top 10 (with ties) other hashtags used in conjunction with `#rstats` (for this search group)?

```{r 03_hash, message=FALSE, warning=FALSE, cache=TRUE}
select(rstats, hashtags) %>% 
  unnest() %>% 
  mutate(hashtags = tolower(hashtags)) %>% 
  count(hashtags, sort=TRUE) %>% 
  filter(hashtags != "rstats") %>% 
  top_n(10)
```

## See Also

- Official Twitter [search API](https://developer.twitter.com/en/docs/tweets/search/guides/build-standard-query) documentation
- Twitter [entites](https://developer.twitter.com/en/docs/tweets/data-dictionary/overview/entities-object) information
- The [tidyverse](https://www.tidyverse.org/) introduction.