# Searching for Tweets

## Problem

You want to collect a sample of tweets from the public timeline for a custom query.

## Solution

Use `rtweet::search_tweets()` and custom [search operators](https://developer.twitter.com/en/docs/tweets/search/guides/standard-operators).

## Discussion

The Twitter API has free and paid tiers. The free tier is what many of us use and there are a number of operators that can be added to a search query to refine the results. We saw one of those in Recipe 3 by using the `#rstats` hashtag in the search query. But there are far more options at our disposal.

We can see all the `#rstats` tweets that aren't retweets:

```{r 04_lib, message=FALSE, warning=FALSE}
library(rtweet)
library(tidyverse)
```
```{r 04_nort, message=FALSE, warning=FALSE, cache=TRUE}
search_tweets("#rstats -filter:retweets") %>%
  select(text)
```

or, all the recent tweet-replies sent to `@kearneymw`:

```{r 04_tomike, message=FALSE, warning=FALSE, cache=TRUE}
search_tweets("to:kearneymw") %>%
  select(text)
```

and, even all the `#rstats` tweets that have GitHub links in them (but no `#python` hashtags):

```{r 04_nopy, message=FALSE, warning=FALSE, cache=TRUE}
search_tweets("#rstats url:github -#python") %>% 
  select(text)
```

## See Also

- Twitter standard [search operators](https://developer.twitter.com/en/docs/tweets/search/guides/standard-operators)