# Harvesting Friends and Followers

## Problem

You want to harvest all of the friends or followers for a particular user.

## Solution

Use `rtweet::get_followers()` or `rtweet::get_friends()`.

## Discussion

The aforementioned `rtweet` functions give us all the data we need and handle pagination and rate-limits.

Let's see who [Brooke Anderson](https://twitter.com/gbwanderson) follows and who follows her. She's an _incredibly talented_ data scientist, weather expert and educator. We'll pull her followers and friends and work with her data a bit more in future recipes.

```{r 13_lib, message=FALSE, warning=FALSE}
library(rtweet)
library(tidyverse)
```
```{r 13_friends, message=FALSE, warning=FALSE, cache=TRUE}
(brooke_followers <- rtweet::get_followers("gbwanderson"))

(brooke_friends <- rtweet::get_friends("gbwanderson"))
```

## See Also

- [Official Twitter API documentation](https://developer.twitter.com/en/docs/accounts-and-users/follow-search-get-users/overview) on friends and followers.